\newpage
\section{Hahn-Banach Theorem}\label{Hahn-Banach Theorem}
One of the most import results in functional analysis, {\bf Hahn-Banach theorem} is a theorem dealing with extending linear maps from a subspace to the whole space. The theorem says that any bounded linear functional defined on a subspace can be  extended to the whole space, while preserving the norm. The result does not rely on completeness of the space, so it's a result for all normed linear spaces. The proof of this theorem involves using a version of \textit{\bf axiom of choice (AC) }, Zorn's lemma. We shall review this lemma first.

\begin{definition}[Partial Order]\rm \nextline
	A partial order on set $X$, is a binary relation, written generically $\leq$, satisfying following property.
	\begin{itemize}
		\item transitivity: if $a\leq b$ and $b\leq c$ then $a\leq c$
		\item reflexivity: $a\leq a$
		\item anti-symmetry: if $a\leq b$ and $b\leq a$ then $a=b$

	\end{itemize}
	If we also have that for any $a$ and $b$, either $a\leq b$ or $b\leq a$, then we say $\leq$ is a total order.

\end{definition}

\begin{definition}[Upper bound]\rm\nextline
	Let $X$ be a set partially ordered by $\leq$ and $Y\subset X$, we say an element $x\in X$ is an {\bf upper bound} of $Y$ if $y\leq x\,\,\forall y\in Y$.

\end{definition}

\begin{definition}[Maximal element]\rm\nextline
	Let $X$ be a set partially ordered by $\leq$ and $Y\subset X$. say $x\in X$ is a maximal element of $X$ if $x\leq m$ implies $m=x$.

\end{definition}
\begin{lemma}[Zorn's lemma]\rm\nextline
	If $X$ is a nonempty partially ordered set with the
	property that every totally ordered subset of $X$ has an upper bound in $X$, then $X$ has
	a maximal element.
\end{lemma}

\begin{theorem}[Hahn-Banach Theorem]\rm\nextline
	Let $X$ be a normed vector space over $\mathbb F$ ($\mathbb{C}$ or $\mathbb{R}$), $Y$ is a proper subspace of $X$. If $T_0:Y\xrightarrow{}\mathbb{F}$ is a bounded linear functional, then there exists a bounded linear functional $T:X\xrightarrow{}\mathbb{F}$ satisfying:
	\begin{itemize}
		\item $T(y)=T_0(y)$ for all $y\in Y$
		\item $\norm{T}=\norm{T_0}$
	\end{itemize}
\end{theorem}
To prove the theorem, the idea is first to show that we can extend linear functional by one dimension, with induction to show that extension can be done to "arbitrarily high dimension". Then by using Zorn's lemma we show that such extension "reaches" every dimension of the space. We first provide real version of the theorem.

\begin{lemma}[one-dimensional extension]\label{ODEX}\rm\nextline
	Let $X$ be a normed vector space over $\mathbb F$ ($\mathbb{C}$ or $\mathbb{R}$), $Y_n$ is a proper subspace of $X$. Let $v\in X\backslash Y$, $X_{n+1}=\{x+hv:x\in X_n,\,h\in\mathbb{C}\}$
	. If $T_n:Y\xrightarrow{}\mathbb{F}$ is a bounded linear functional, then there exists a bounded linear functional $T_{n+1}:X_{n+1}\xrightarrow{}\mathbb{F}$ satisfying:
	\begin{itemize}
		\item $T_{n+1}(x)=T_n(x)$ for all $x\in X_n$
		\item $\norm{T_{n+1}}=\norm{T_n}$
	\end{itemize}
	\begin{pf}{One-dimensional extension}{}
		Define linear functional $P:X_{n+1}\xrightarrow{}\mathbb{R}$ by
		$$
			P(x+kv)=T_n(x)-Ck,\,\forall\,x\in X_n,\,k\in\mathbb{R}
		$$
		where C is a constant to be determined.
		First we shall check linearity, which is left as an exercise.
		Then we shall show that we can find a proper constant $C$ so that $\norm{P}=\norm{T_n}$. Note that $X_n\subset X_{n+1}$, so we have
		\begin{equation}
			\begin{split}
				\norm{P}&=\sup_{x\in X_{n+1}}(\{|Px|:\norm{x}=1\})\\
				&\geq\sup_{x\in X_{n}}(\{|Px|:\norm{x}=1\})\\
				&=\sup_{x\in X_{n}}(\{|T_nx|:\norm{x}=1\})\\
				&=1
			\end{split}
		\end{equation}
		So by choosing $C$ such that $P(x+kv)\leq \norm{x+kv}$ for any $x\in X_n$ and $k\in \mathbb{R}$, we will have that $\norm{P}\leq 1$, giving $\norm{P}=1$. Thus it remains to show that we can find such a constant $C$.\\
		We aim to find $C$ such that
		$$
			|P(x+kv)|=|T_n(x)-Ck|\leq \norm{x+kv},\,\forall x\in X_n,\,\forall k\in\mathbb{R}
		$$
		Hence,
		$$
			T_n(x)-\norm{x+kv}\leq Ck\leq T_n(x)+\norm{x+kv},\,\forall x\in X_n,\,\forall k\in\mathbb{R}
		$$
		Note that for all $x,y\in X_n$ we have:
		\begin{equation}
			\begin{split}
				T_nx-T_ny&=T_n(x-y)\\
				&\leq \norm{x-y}\\
				&=\norm{(x+kv)-(kv+y)}\\
				&\leq\norm{x+kv}+\norm{y+kv}
			\end{split}
		\end{equation}
		Thus
		$$
			l^-=\sup_{x\in X_n,k\in\mathbb{R}}(T_n(x)-\norm{x+kv})\leq  \inf_{x\in X_n,k\in\mathbb{R}}(T_n(x)+\norm{x+kv})=l^+
		$$
		Hence we can always find a $C$ such that
		$$
			T_n(x)-\norm{x+kv}\leq l^-\leq Ck\leq l^+ \leq T_n(x)+\norm{x+kv},\,\forall x\in X_n,\,\forall k\in\mathbb{R}
		$$
		Which finishes the proof.
	\end{pf}
\end{lemma}
\subsection{Proof of Hahn-Banach theorem,real case}
Starting from $T_0:Y\xrightarrow{}\mathbb{R}$, by \ref{ODEX} we can define  $T_{n+1}$ to be the one-dimensional extension of $T_n$ for any $n\in\mathbb{N}$, with domain $Y_{n+1}$ extended from $Y_n$, for convenience we let$Y_0=Y$.
Then consider the set
$$
	M=
	\left\{
	(T_n,Y_n),n\in\mathbb{N}
	\right\}
$$
which can be partially ordered by $\leq$ defined as
$$
	(T_a,Y_a)\leq(T_b,Y_b)\,\text{ if } Y_a\subset Y_b,\,\text{ and } T_b=T_a\, \text{ on }\, Y_a
$$
Now let $S=\{(T_i,Y_i),i\in I\}$ (where $I$ is the index set) be a totally ordered subset of $M$. Consider $Y'=\cup_{i\in I}Y_i$ with $T'(x)=T_i(x)$ if $x\in Y_i$, we have that $(T',Y')\in M$ is an upper bound of $S$. By Zorn's lemma, we know that $M$ has a maximal element, denoted as $(T_\infty,Y_\infty)$. We claim that $Y_\infty=X$, because if not, we can do one-dimensional extension to $Y_\infty$, resulting in $X\subset Y_\infty+1$, contradicting with maximality. Thus we have $Y_\infty=X$, and  $T_\infty$ is the desired extension to $X$.

\subsection{Proof of Hahn-Banach theorem,complex case}
To prove the statement for complex case, we shall exploit a connection between real valued functional and complex one.\\
\begin{proposition}\rm\nextline
	Let $T:X\xrightarrow{}\mathbb{C}$ be a complex linear functional. Define $u(x)=Re(T(x))$ for all $x\in X$. Then
	\begin{itemize}
		\item $u(x)$ is a real-valued linear functional
		\item $T(x)=u(x)-iu(ix)$
		\item $\norm{u}=\norm{T}$
	\end{itemize}
	Moreover, given any linear functional $u(x)$, $T(x)=u(x)-iu(ix)$ defines a complex linear functional
	\begin{pf}{}{}

	The first two are very easy to show. The hardest part is on the third statement. We first show that $\norm{T}\geq\norm{u}$:
	\begin{equation}
		\begin{split}
			\norm{T}^2&=\sup\{|T x|^2,\norm{x}=1\}\\
			&=\sup\{|u(x)-iu(ix)|^2,\norm{x}=1\}\\
			&=\sup \{[u(x)]^2+[u(ix)]^2,\norm{x}=1\}\\
			&\geq \sup \{[u(x)]^2,\norm{x}=1\}\\
			&=\norm{u}^2
		\end{split}
	\end{equation}
	On the other hand, pick any $x\in X$ with $\norm{x}=1$, denote $T(x)=re^{i\theta}$, we have
	$$|T(x)|=|e^{-i\theta}||T(x)|=|T(e^{-i\theta}x)|=|u(e^{-i\theta}x)-iu(e^{-i\theta}x)|$$
	\begin{equation}
		\begin{split}
			|T(x)|&=|e^{-i\theta}||T(x)|\\
			&=|T(e^{-i\theta}x)|\\
			&=|u(e^{-i\theta}x)-iu(e^{-i\theta}x)|
		\end{split}
	\end{equation}
	But we have that $T(e^{-i\theta}x)=r\in\mathbb{R}$, thus
	$$
		|T(e^{-i\theta}x)|=|Re(T(e^{-i\theta}x))|=|u(e^{-i\theta}x)|\leq\norm{u}
	$$
	Hence $\norm{T}=\norm{u}$.
\end{pf}
\end{proposition}
The remaining part of the proof is simply combining last result and the proof of real case. However, last result also gives a insight on complex bounded linear functional

\subsection{Hahn-Banach with sublinear function}
Previous discussion of Hahn Banach theorem considers extension preserving norm. However, we can consider extension in a more general setting, namely sublinear.
\begin{definition}[sublinear function]\label{sublinear map}\rm\nextline
	Let $X$ be a vector space. \func{p}{X}{\real} is a sublinear function if the following holdsL
	\begin{itemize}
		\item $p(kx)=kp(x),$ for all $x\in X$ and $k\geq0$
		\item $p(x+y)=p(x)+p(y),\,\,\forall x,y\in X$
	\end{itemize}
\end{definition}

\begin{definition}[Restriction]\rm\nextline
	Let \func{f}{X}{Y}. Let $S\subset X$, if \func{g}{M}{Y} is such that $g(x)=f(x),\,\,\forall x\in M$ then we say $f$ restricted to $M$ is $g$, denoted by $g=f|_M$
\end{definition}
\begin{theorem}[Hahn-Banach Theorem, sublinear]\rm\nextline
	Let $M\in X$ be a linear subspace of $X$, where $X$ is a linear space. \func{p}{X}{\real} is sublinear, and \func{f}{M}{\real} is a linear map such that $f(x)\leq p(x),\,\,\forall x\in M$.\\
	Then, there exists a linear map \func{F}{X}{\real} with $F|_M=f$ and $F(x)\leq p(x),\,\,\forall x\in M$.
	\begin{pf}{Hahn-Banach Theorem, sublinear}{}
		\placeholder
	\end{pf}
\end{theorem}

\subsection{Results of Hahn-Banach}
\begin{theorem}[Dual functional]\label{Dual functional}\rm\nextline
	Let $X$ be a normed linear space. $\forall x\in X,\,\exists x^*\in \dual{X}$ s.t. $\inne{\dual{x}}{x}\equiv\dual{x}(x)=\norm{x}^2_X=\norm{\dual{x}}^2_{\dual{X}}$\\
	Note that here $\inne{\cdot}{\cdot}$ does not necessarily stand for inner product.
	\begin{pf}{Dual functional}{}
		Let $M=span(x)$. Define $f(tx)=t\norm{x}^2_X,\,\,\forall t\in \real$. Clearly $f$ is linear, and that $\norm{f}_{\dual{M}}=\norm{x}_X$. \\
		Then we apply Hahn-Banach theorem to extend $f$ to $\dual{x}=F\in \dual{X}$, with $\norm{\dual{x}}_{\dual{X}}=\norm{f}_M=\norm{x}_X$
	\end{pf}
\end{theorem}
When the space is a Hilbert space, this theorem becomes Riesz representation theorem. (without changing notation! That's why bracket is a good notation here) In short, this theorem says that you can always find a linear functional such that for its value for a chosen element is precisely the norm of this element.

\begin{proposition}[Point-point separation]\label{separations}\rm\nextline
	Let $x$ and $y$ be points in $X$ \placeholder \\
	(Question here is do  we need X to be normed? or even Banach?)
	There exists $l\in\dual{X}$ such that $l(x)\neq l(y)$.
	\begin{pf}{}{}
		Choose $l\in \dual{X}$ to be the dual functional of $(y-x)\in X$. \\Then $l(y-x)=\norm{y-x}^2_X>0\implies l(y)\neq l(x)$.
	\end{pf}
\end{proposition}

\begin{proposition}[separation from proper closed subspaces]\rm\nextline
$M\subset X$ is a linear space, closed and (naturally) convex, Assume $x_0\not\in M$ such that $d\equiv dist(x_0,M)$, then $\exists \ell\in\dual{X}$ with $\ell|_M=0$ and $\norm{\ell}_\dual{X}=1$ and $\ell(x_0)=d$.
\begin{pf}{}{}
	Let $M_0=\{xt+x_0:x\in M\}$. Define \func{f}{M_0}{\real} which is linear, $f(x+tx_0)=td$. Then\\
	\placeholder
\end{pf}
\end{proposition}